### 2015-03-02 README.Rmd
added coveralls badge to readme

[![Build Status](https://api.travis-ci.org/ropensci/taxize.png?branch=master)](https://travis-ci.org/ropensci/taxize)
[![Build status](https://ci.appveyor.com/api/projects/status/6mgc02mkd8j4sq3g/branch/master)](https://ci.appveyor.com/project/sckott/taxize-175/branch/master)

>>>>

[![Build Status](https://api.travis-ci.org/ropensci/taxize.png?branch=master)](https://travis-ci.org/ropensci/taxize)
[![Build status](https://ci.appveyor.com/api/projects/status/6mgc02mkd8j4sq3g/branch/master)](https://ci.appveyor.com/project/sckott/taxize-175/branch/master)
[![Coverage Status](https://coveralls.io/repos/ropensci/taxize/badge.svg)](https://coveralls.io/r/ropensci/taxize)
